### 2020-05-23 system-model.tex
:construction: Transmit and receive signal

	\begin{subsection}{Transmitted Signal}
		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
		\begin{subsubsection} {Modulated Information Waveform}
			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ over subband $n$, which follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$. The transmit information signal at time $t$ is
			\begin{equation}\label{eq:x_I}
				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I,n}=s_{I,n}e^{j\phi_{I,n}}$ collects the magnitude and phase of the information signal at frequency $n$. We further define the information waveform vector $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

		\begin{subsubsection}{Unmodulated Power Waveform}
			With no randomness over time, the transmit power signal is
			\begin{equation}\label{eq:x_P}
				x_{P}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}$ includes the magnitude and phase of the $n$-th tone. Also, define the power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

		\begin{subsubsection}{Superposed Waveform}
			The transmit signal at time $t$ over subband $n$ is
			\begin{equation}\label{eq:x_n(t)}
				x_n(t)=\sum_{k=1}^K{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
			\end{equation}
			Hence, the transmitted RF signal is
			\begin{equation}\label{eq:x(t)}
				x(t)=\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
				% x(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}\right\}
			\end{equation}
		\end{subsubsection}
	\end{subsection}

@@

	\begin{subsection}{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k(t)}
			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}}(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n}){e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		with the information and power components of
		\begin{equation}\label{eq:y_{I,k}(t)}
			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{I,j,n}\tilde{x}_{I,j,n}}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}
		\begin{equation}\label{eq:y_{P,k}(t)}
			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{P,j,n}}{e^{j2{\pi}{f_n}{t}}}
		\end{equation}

>>>>

	\begin{subsection}{Transmit Signal}
		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
		\begin{subsubsection} {Modulated Information Waveform}
			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ over subband $n$, which follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$. The transmit information signal at time $t$ is
			\begin{equation}\label{eq:x_I}
				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I,k,n}=s_{I,k,n}e^{j\phi_{I,k,n}}$ collects the magnitude and phase of the information signal of user $k$ at frequency $n$. We further define the information waveform vector $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

		\begin{subsubsection}{Unmodulated Power Waveform}
			With no randomness over time, the transmit power signal is
			\begin{equation}\label{eq:x_P}
				x_{P}=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}}{e^{j2{\pi}{f_n}{t}}}\right\}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}=\sum_{k=1}^K{w_{P,k,n}}$ combines the magnitude and phase on the $n$-th power tone over all users. Also, collect $w_{P,n}$ into power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

		Therefore, the superposed transmit signal at time $t$ over subband $n$ is
		\begin{equation}\label{eq:x}
			x(t)=\Re\left\{\sum_{n=1}^N\left(\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}

@@

	\begin{subsection}{Receive Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k}
			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left(\sum_{j=1}^K{w_{I,j,n}\tilde{x}_{I,j,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}
	\end{subsection}
